---
title: "P8105-HW3-zc2556"
author: "Zhe Chen"
date: "2020/10/10"
output: github_document
---

## Problem 1

### Include Relevent Libraries

```{r, warning=FALSE}
library(tidyverse)
library(p8105.datasets)
```


### Implement Some Default Settings

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(
  theme_minimal()+
  theme(legend.position = "bottom")
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continous.fill = "viridis"
)

scale_color_discrete = scale_colour_viridis_d()
scale_fill_discrete = scale_fill_viridis_d

```

### Basic Description of the Data Set

```{r}
data("instacart")
```

The data contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. Each observations are assigned with the number of items and user ID. We have information about order/order ID, days and hours. Also, we have item information, like name, aisle, department and codes.


### Answering Questions

#### Aisles

```{r}
#count for the number of aisles and find the most popular aisle
instacart %>%
  count(aisle) %>%
  arrange(desc(n))
```
We can see there are 134 different aisles and "fresh vegetables" has the most items.

#### Plot

```{r}
instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n) #rearrange the frame
  ) %>%
  ggplot(aes(x = aisle, y = n))+
  geom_point()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

#### Make a Table of Targeted Aisles

```{r}
instacart %>%
  filter( aisle %in% c("baking ingredients", "dog food care","packaged vegetables fruits"))%>%
  group_by(aisle)%>%
  count(product_name)%>%
  mutate(
    rank = min_rank(desc(n))
  )%>%
  filter(rank < 4) %>%
  arrange(aisle, rank)%>%
  knitr::kable()
```

#### Make a Table Showing the Mean Hour of the Day between "Apples" and "Ice Cream"

```{r}
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow)%>%
  summarise(mean_hour = mean(order_hour_of_day))%>%
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  )
  
```






















